### 2018-11-12 Sections/essays_quantum_ecosystem.tex
minor
Ecosystems figure added

@@

\begin{itemize}
\item Oracles: As an essential quantum software building block, oracles will become a fundamental unit for outsourcing. These oracles will store hard-corded or algorithmically-generated databases. For example, for use in genetic medicine (Sec.~\ref{sec:genetic_medicine}), such databases could algorithmically generate tables of candidate drug compounds, or they could implement mathematical functions whose input space is to be searched over when quantum-enhancing the solving of \textbf{NP}-complete problems.
\item Interfacing: \textit{De facto} standards will emerge for interconnecting quantum hardware units. Most notably, standards for optical interconnects will arise.
\item Modularisation: Arbitrarily-interconnectable units will develop, allowing quantum hardware to be constructed in an ad hoc, Lego-like\index{Lego} manner. These modules could implement small elements of a larger quantum computation, such as housing a small part of a larger graph state (Sec.~\ref{sec:module}), communications building blocks (such as transmitters or receivers of Bell-pairs), or algorithmic building blocks such as quantum Fourier transforms (Sec.~\ref{sec:QFT_alg}).
\end{itemize}

>>>>

\famousquote{The most dangerous worldview is the worldview of those who have not viewed the world.}{Alexander von Humboldt}
\newline

@@

\comment{To do}

\begin{itemize}
\item Quantum operations: vendors selling the capacity for non-trivial state preparation (e.g NOON\index{NOON states} and states GHZ\index{GHZ states}), or measurements (e.g complex syndrome measurements).

\item Software subroutines:\index{Subroutines} Much like classical code, many quantum computations (and other quantum protocols) can be decomposed into pipelines of quantum subroutines. There are many quantum operations that arise repeatedly (such as quantum Fourier transforms and syndrome calculations), which vendors might specialise in for outsourcing.

\item Oracles:\index{Oracles} As an essential quantum software building block, oracles will become a fundamental unit for outsourcing. These oracles will store hard-corded or algorithmically-generated databases. For example, for use in genetic medicine (Sec.~\ref{sec:genetic_medicine}), such databases could algorithmically generate tables of candidate drug compounds, or they could implement mathematical functions whose input space is to be searched over when quantum-enhancing the solving of \textbf{NP}-complete\index{NP and NP-complete} problems.

\item Interfacing:\index{Interfacing} \textit{De facto} standards will emerge for interconnecting quantum hardware units. Most notably, standards for optical interconnects will arise.

\item Modularisation:\index{Modularisation} Arbitrarily-interconnectable units will develop, allowing quantum hardware to be constructed in an ad hoc, Lego-like\index{Lego} manner. These modules could implement small elements of a larger quantum computation, such as housing a small part of a larger graph state (Sec.~\ref{sec:module}), communications building blocks (such as transmitters or receivers of Bell-pairs), or algorithmic building blocks such as quantum Fourier transforms (Sec.~\ref{sec:QFT_alg}).

\item Classical pre-, post- or intermediate-processing:\index{Classical processing} Quantum computation, and other quantum protocols, typically require some degree of classical pre- or post-processing, or feedforward. These classical operations can be highly non-trivial. For example, a novel topological quantum error correcting code\index{Quantum error correction} (Sec.~\ref{sec:surface_codes}) might require complex encoding, decoding and feedforward operations. Determining and implementing these operations may require complicated optimisation protocols. These might be outsourced to a specialised provider.
\end{itemize}

A map of just a few of the potential elements to emerge in the quantum ecosystem is presented in Fig.~\ref{fig:ecosystem}.

\begin{figure}[!htpb]
\if 2\pubmode
\includegraphics[clip=true, width=0.475\textwidth]{ecosystem_long}
\else
\includegraphics[clip=true, width=\textwidth]{ecosystem}
\fi
\caption{Map of just a few of the elements of the quantum ecosystem that are likely to arise with the advent of the quantum internet. The distinct units could become areas of specialisation for quantum software/hardware vendors, which might be licensed out or sold to customers as discrete units, or as complete integrated processing pipelines.}\label{fig:ecosystem}\index{Quantum ecosystem}	
\end{figure}
